---
title: "intc"
author: "ANelson"
date: "November 6, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This exercise explores working with time series analysis on the stock price of Intel Corp data (INTC). The raw data was obtained from Yahoo Finance covering the data range of 11/6/2005 to 11/6/2017. This analysis uses the fpp package, and tseries package.

###Create the dataframe
```{r createts, include=TRUE, echo=TRUE }
library(fpp)
library(tseries)

getwd()
list.files()
intcraw<- read.csv("intc.csv")

head(intcraw)
str(intcraw)
#convert the dataframw to a Time Series
intcraw <- ts(intcraw)
str(intcraw)
```
###Explore the time series

```{r explore, include=TRUE, echo=TRUE }
summary(intcraw)
plot(intcraw)
```
##Observations: 
**1)The variables open, high, low,close, adjClose, and Volume have similar trends, ie they track each other with similar, insynch data patterns with respect to time.**
**2)There is a general upward trend beginning around time = 800 and continuing thru to the end of the dataset.**
**3)The start of the general upward trend is at the end of downward trend which starts at the beginning of the dataset.**

###Log Returns amd log Volume
```{r logreturns, include=TRUE, echo=TRUE }
intcdf <- as.data.frame(intcraw)
intcdf$logreturn <- c(diff(log(intcdf$Close)),NA)
intcdf$logvolume <- log(intcdf$Volume)
intcts <- ts(intcdf)

plot(intcts)


```
###Volatility Measure
```{r vm, include=TRUE, echo=TRUE }
vm <- sd(intcdf$logreturn,na.rm=TRUE)*sqrt(250)* 100
vm
```
###Volatility Measures for lookback windows
```{r vmlookback, include=TRUE, echo=TRUE }
Vol <- function(d,logrets) {
var=0
lam=0
varlist <- c()
for (r in logrets) {
lam=lam*(1-1/d) + 1
var=(1-1/lam)*var + (1/lam)*r^2
varlist <- c(varlist,var)
}
sqrt(varlist)}
volest0 <- Vol(1,intcdf$logreturn)
volest <- Vol(10,intcdf$logreturn)
volest2 <- Vol(30,intcdf$logreturn)
volest3 <- Vol(100,intcdf$logreturn)


plot(volest0,type="l",main="Volatility Estimates for INTC 11/6/2005 - 11/6/2017")
lines(volest, type="l",col="orange")
lines(volest2,type="l",col="red")
lines(volest3,type="l",col="green")

```
** Black is the log return actuals.  The orange (.9 weight) and red (.7 weight) fit the actual distribution pretty well...not much smoothing.  The green distrubtion (weight .99) is much smoother. **